Figures to insert in text

### 2018-03-05 Chapters/sdm2.tex
Parts under work

  \subfloat[$Q_{10}$]{\includegraphics[width=4.0in]{./images02/new-images/qn10.png}}
  \caption{Here we have $Q_n$, for $n \in$ \{3, 7, 10\}. Each node represents a possible bitstring in $\{0,1\}^n$, and two nodes are linked if the bitstrings differ by a single dimension.  A number of observations can be made here. First, the number of nodes grows as $2^n$ as $n$ grows; which makes the  space intractable as $n>>20$. Another interesting observation, better seen in the figures below, is that most of the space lies `at the center', at a distance of around 500 from any given vantage point.\label{hypercubes}}
\end{figure}

The graph composed of $\{0,1\}^n$ nodes and links between nodes $iff$ their Hamming distance is one is called the \emph{hypercube graph}, or $Q_n$, as in Figure \ref{hypercubes}.  Though Kanerva has derived many combinatorial properties of the space, I believe that this is a aesthetically appealing object on its own, and beautiful results can be found in the graph-theoretical literature. A good survey is found in \citet{harary1988survey}.

>>>>

  \subfloat[$Q_{10}$]{\includegraphics[width=4.0in]{./images02/new-images/qn10.png}}
  \caption{Here we have $Q_n$, for $n \in$ \{3, 7, 10\}. Each node corresponds to a bitstring in $\{0,1\}^n$, and two nodes are linked iff the bitstrings differ by a single dimension.  A number of observations can be made here. First, the number of nodes grows as $2^n$ as $n$ grows; which makes the  space intractable as $n>>20$. Another interesting observation, better seen in the figures below, is that most of the space lies `at the center', at a distance of around 500 from any given vantage point.\label{hypercubes}}
\end{figure}

The space studied by Kanerva is also called the \emph{hypercube graph}, or $Q_n$, as in Figure \ref{hypercubes}. For a fixed $n \in \mathbb{Z}$, the graph $G = (V, E)$, in which $v \in V$ iff there is a bijective function $b: V\to \{0,1\}^n$ and $(v_i, v_j) \in E$ iff $H(b(v_i), b(v_j))=1$, where $H$ is the Hamming distance. That is, $n$-sized bitstrings correspond to nodes and edges exist between nodes $iff$ they flip a single bit.  Though Kanerva has derived many combinatorial properties of the space, additional results have been found in the graph-theoretical literature. A good survey is provided by \citet{harary1988survey}.
